Measuring directionality in double-beta decay and neutrino interactions with kiloton-scale scintillation detectors

### 2014-04-21 Direction_JINST_v11.1.tex
Add old versions of paper. --Lindley

The Cherenkov light produced at wavelengths shorter than the
absorption cutoff of the scintillator will be absorbed and re-emitted
as isotropic light, but wavelengths longer than this cutoff will
propagate across the detector, retaining their directional
information. The absorption cutoff for the example scintillator above is 370~nm. The index of refraction at $\lambda$=370~nm is n=1.466, which translates
%n(370nm)=1.466 and can be translated 
into an effective Cherenkov threshold for electrons at 0.188~MeV. For a 5~MeV electron, this yields 685 Cherenkov photons per event when integrating from the cutoff wavelength at 370~nm to 550~nm,  the wavelength above which a small number of photons is detected due to a standard bialkali photocathode's quantum efficiency. Lowering the energy to 1~MeV yields 82 Cherenkov photons between 370-550~nm.

@@

The two additional simulation sets with 1.4 MeV and 2.1 MeV electrons were
generated using the default simulation configuration described in section
\ref{sim_section}. The PE time distribution for the default settings is shown
in figure \ref{time_plots_comparison} (a) for 5~MeV electrons. The shapes
of the scintillation and Cherenkov spectra are similar for the lower energies (not
shown here). In figure \ref{Edep_NPE}, the energy-dependent mean number of
PEs per event after the 34.0~ns time cut is shown for Cherenkov-induced and
scintillation-induced PEs, as well as their ratio $R_{C/S}$. The mean number
of PEs from Cherenkov (scintillation) light for electron energies of 1.4, 2.1, and 5~MeV is 21.8 (52.1), 38.4 (76.8)
and 108 (171) for 1.4~MeV, 2.1~MeV and 5~MeV, respectively. This gives the
ratios $R_{C/S}$ = 0.42, 0.50 and 0.63: The decrease in Cherenkov-induced
PEs is stronger than the decrease in scintillation-induced PEs as the energy
is lowered.

>>>>

The Cherenkov light produced at wavelengths shorter than the
absorption cutoff of the scintillator will be absorbed and re-emitted
as isotropic light, but wavelengths longer than this cutoff will
propagate across the detector, retaining their directional
information. The absorption cutoff for the example scintillator above is 370~nm. The index of refraction at $\lambda$=370~nm is n=1.466, which translates
%n(370nm)=1.466 and can be translated 
into an effective Cherenkov threshold for electrons at 0.188~MeV. For a 5~MeV electron, this yields 685 Cherenkov photons per event when integrating from the cutoff wavelength at 370~nm to 550~nm,  the wavelength above which a small number of photons is detected due to the quantum efficiency of a standard bialkali photocathode. Lowering the energy to 1~MeV yields 82 Cherenkov photons between 370-550~nm.

@@

The two additional simulation sets with 1.4 MeV and 2.1 MeV electrons were
generated using the default simulation configuration described in section
\ref{sim_section}. The PE time distribution for the default settings is shown
in figure \ref{time_plots_comparison} (a) for 5~MeV electrons. The shapes
of the scintillation and Cherenkov spectra are similar for the lower energies (not
shown here). In figure \ref{Edep_NPE}, the energy-dependent mean number of
PEs per event after the 34.0~ns time cut is shown for Cherenkov-induced and
scintillation-induced PEs, as well as their ratio $R_{C/S}$. The mean number
of PEs from Cherenkov (scintillation) light is 21.8 (52.1), 38.4 (76.8)
and 108 (171) for electron energies of 1.4~MeV, 2.1~MeV and 5~MeV, respectively. This gives the
ratios $R_{C/S}$ = 0.42, 0.50 and 0.63: The decrease in Cherenkov-induced
PEs is stronger than the decrease in scintillation-induced PEs as the energy
is lowered.
